\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{mathtools}

\usepackage{euscript}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\title{Random Equations}
\author{willpowe}
\date{September 2021}

\begin{document}
\section{Model}


\begin{equation}
x_{n,t}^k= f_{\text{Update}}(
						f_{\text{Agg}}^C(\textbf{N}_{n,t}^{k-1}),
						f_{\text{Agg}}^S(\textbf{S}_{n,t}^{k-1}),
						f_{\text{Agg}}^T(x_{n,t-1}^{k-1}, \cdots, x_{n, t-d}^{k-1}), 
						x_{n, t}^{k-1})
\end{equation}

Where \\
\\
$f_{\text{Agg}}^C$ is the county-timestep-layer aggregation function. \\
$f_{\text{Agg}}^S$ is the subreddit-layer aggregation function. \\
$f_{\text{Agg}}^T$ is the temporal aggregation function.  \\
\\
The aggregation functions operate on the preceeding iterations messages, from the $(k-1)^\text{th}$ step of updates. The temporal aspect of the data is encoded in the parameters to the temporal temporal aggregation function. In this formaulation, there is a single, large graph with a node for each county, at each timestep. The temporal parameters represent the connections between different temporal realizations of a given county. In a sense, each node has a directional connection to $d$ nodes `in the past'.

\subsection{$f_{\text{Agg}}^C$}
The parameters to this function represent the connections for a single county node $n$ at a single timestep $t$. The set $\textbf{N}_{n,t}^{k-1}$ contains the messages from the neighborhood of the county node $n$ at the same timestep, from the preceeding round of updates. 
\\
A draft approach would be to use \textbf{symmetric normalization}, and sum the set of messages, each weighted by the factor $\frac{1}{\sqrt{\EuScript{N}_u*\EuScript{N}_v}}$\\

$$f_{\text{Agg}}^C(\textbf{N}_{n,t}^{k-1})=\sum_v^{\textbf{N}}\left( \frac{x_{v,t}^{k-1}}{\sqrt{\EuScript{N}_v*\EuScript{N}_n}} \right)$$

This could be improved by the use of `deep' methods, where a small parameterized function or network could be used to aggregate the messages. 

\subsection{$f_{\text{Agg}}^S$}
The parameters to this function represent the connections between a single county-node $n$ at a single timestep $t$ and the set of `static' subreddit nodes. The term static is used to refer to the fact that there is only a single node for a given subreddit, not a node for each timestep. \\
The set $\textbf{S}_{n,t}^{k-1}$ represents the set of messages from all subreddits connected to the county at that timestep, from the preceeding iteration of the update function.\\
The message sent by a subreddit is simply a parameter holding its current `embedding' in some low dimensional space, weighted by the edge weight (actual count value from the counties reddit activity for that timestep). For a subreddit $s$, its message to node $n$ will be a function:
$$\textbf{m}_{n,t,s}^{k} = x_{s}^{k-1}*g(e_{n,t,s})$$\\
Where $x_{s}^{k-1} \in \EuScript{R}^i$ is the state of the subreddit in the preceeding iteration of message passing, and $i$ is the chosen dimension of the embedding space for subreddits. The function $g$ weights this message by the value of the edge between the subreddit and the county node at that timestep, $e_{n,t,s}$
\\
To aggregate these, the \textbf{Set Pooling} method would be used, where two MLPs are trained, with one operating directly on subreddit state values, and the second oeprating on the sum of these.

$$f_{\text{Agg}}^S(\textbf{S}_{n,t}^{k-1})=\text{MLP}_{\theta}\left(\sum_{s}^{S}\text{MLP}_\phi\left(\textbf{m}_{n,t,s}^{k-1}\right)\right)$$

The weight values for the $\phi$ MLP would be shared across all subreddits. 

\subsection{$f_{\text{Agg}}^T$}
This function encodes the temporal history of a specific node, at a specific timestep. The sequence $x_{n,t-1}^{k-1}, \cdots, x_{n, t-d}^{k-1}$ represents the $d$ nodes associated with county $n$, at the $d$ preceeding timesteps. \\
To handle the sequential nature of this data, the a draft aggregation function could be an LSTM model.

$$f_{\text{Agg}}^T(x_{n,t-1}^{k-1}, \cdots, x_{n, t-d}^{k-1}) = \text{LSTM}(x_{n,t-1}^{k-1}, \cdots, x_{n, t-d}^{k-1})$$



\end{document}